---
output:
  rmarkdown::github_document:
    html_preview: no
---

```{r, include = FALSE}
knitr::opts_chunk$set(fig.path = "man/figures/README-", fig.align = "center",
                      fig.height = 4.5, fig.width = 4.5)
```

<!--- README.md is generated from README.Rmd. Please edit that file -->

## prepairr: Interface to prepair
[![lifecycle](https://img.shields.io/badge/Lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis Build Status](https://img.shields.io/travis/jeffreyhanson/prepairr/master.svg?label=Linux%20%26%20Mac%20OSX)](https://travis-ci.org/jeffreyhanson/prepairr)
[![Coverage Status](https://codecov.io/github/jeffreyhanson/prepairr/coverage.svg?branch=master)](https://codecov.io/github/jeffreyhanson/prepairr?branch=master)

```{r, include = FALSE}
devtools::load_all()
```

### Overview

The _prepairr R_ package provides an interface to the [_prepair_ tool](https://github.com/tudelft3d/prepair) for repairing invalid polygon geometries (Ledoux, Arroyo Ohori & Meijers, 2014). This project was developed as an experiment to benchmark the performance of the _prepair_ tool for repairing invalid geometries in large spatial datasets. Unfortunately, this package is actually **slower** than standard geometry cleaning tools (such as the [_lwgeom R package_]([_lwgeom R_ package](https://CRAN.R-project.org/package=lwgeom)). As a consequence, this package is unlikely to receive further development.

### Installation

The developmental version of the _prepairr R_ package can be installed using the following R code. Please note that this package will only work on Unix systems and requires the [_sf R_](https://github.com/r-spatial/sf) package which requires additional software to be installed. If you encounter problems installing the _prepairr R_ package, please consult the installation instructions for the [_sf R_](https://github.com/r-spatial/sf) package.

```{r, eval = FALSE}
if (!require(remotes))
  remotes::install_github("jeffreyhanson/prepairr")
```

### Usage

Here we will explore the usage and (substandard) performance of this package. To achieve this, we will first load the _prepair_ package. We will also load two other packages for working with spatial vector data.

```{r}
# load packages
library(prepairr)
library(sf)
library(lwgeom)
library(rworldxtra)
```

Next, we will obtain a spatial dataset containing invalid geometries. Specifically, we will import data delineating the country boundaries (originally from [Natural Earth](https://www.naturalearthdata.com/)).

```{r}
# import data, subset data to reduce total run time, and convert to sf format
data(countriesHigh, package = "rworldxtra")
x <- as(countriesHigh[c(12, 41, 132), ], "sf")

# preview data
print(x)

# plot data
plot(st_geometry(x), main = "raw data")

# verify that the dataset has invalid geometries
all(suppressWarnings(st_is_valid(x)))
```

Now we will repair the data using the [_prepair_ tool](https://github.com/tudelft3d/prepair). We will also record how long it takes to repair the data so we can compare it with standard data cleaning tools later.

```{r}
# repair geometries using prepair and record processing time
prepair_time <- system.time({
  y <- st_prepair(x)
})[[3]]

# preview cleaned data
print(y)

# verify that all geometries are now valid
all(st_is_valid(y))

# print processing time (seconds)
print(prepair_time)

# plot repaired data
plot(st_geometry(y), main = "repaired data")
```

Next we will repair the data using the [_lwgeom R_ package](https://CRAN.R-project.org/package=lwgeom) and record how long this tool takes to repair the data.

```{r}
# repair geometries using lwgeom and record processing time
lwgeom_time <- system.time({
  z <- st-make_valid(x)
})[[3]]

# preview cleaned data
print(z)

# verify that all geometries are now valid
all(st_is_valid(z))

# print processing time (seconds)
print(lwgeom_time)
```

As we can see, the `st_prepair` function in this package took `r prepair_time - lwgeom_time` seconds longer to complete. Therefore, do not use this package to clean your data.


### References

[Ledoux H, Arroyo Ohori K, and Meijers M (2014) A triangulation-based approach to automatically repair GIS polygons. Computers & Geosciences 66:121--131](https://doi.org/10.1016/j.cageo.2014.01.009).

### Citation

This is an experimental package. You should not be citing this package because you should not be using it for any reason at all.
