---
output:
  rmarkdown::github_document:
    html_preview: no
---

```{r, include = FALSE}
knitr::opts_chunk$set(fig.path = "man/figures/README-", fig.align = "center",
                      fig.height = 4.5, fig.width = 4.5)
```

<!--- README.md is generated from README.Rmd. Please edit that file -->

## prepairr: Interface to prepair
[![lifecycle](https://img.shields.io/badge/Lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis Build Status](https://img.shields.io/travis/jeffreyhanson/prepairr/master.svg?label=Linux%20%26%20Mac%20OSX)](https://travis-ci.org/jeffreyhanson/prepairr)
[![AppVeyor Build Status](https://img.shields.io/appveyor/ci/jeffreyhanson/prepairr/master.svg?label=Windows)](https://ci.appveyor.com/project/jeffreyhanson/prepairr)
[![Coverage Status](https://codecov.io/github/jeffreyhanson/prepairr/coverage.svg?branch=master)](https://codecov.io/github/jeffreyhanson/prepairr?branch=master)

```{r, include = FALSE}
devtools::load_all()
```

### Overview

TODO.

### Installation

The developmental version of the _prepairr R_ package can be installed using the following R code. Please note that this package requires the [_sf R_](https://github.com/r-spatial/sf) package which may require additional software to be installed. If you encounter problems installing the _prepairr R_ package, please consult the installation instructions for this packages.

```{r, eval = FALSE}
if (!require(remotes))
  remotes::install_github("jeffreyhanson/prepairr")
```

### Usage

TODO.

### Citation

This is an experimental package. You should not be citing this package because you should not be using it for any serious work.
